Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
comments to myself
first para of intro

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -JS
  \\---\\
  Will fix grammar after fixing all other problems -KC}
\todo[inline]{The first paragraph of the introduction should summarize
  the entire introduction, and in some sense, the entire paper. -JS}

Around 2006, many work on integrating dynamic typing and static typing emerge, 
notably gradual types \citep{siek2006gradual} and hybrid types 
\citep{flanagan2006hybrid}. The semantics of gradually typed languages is 
usuallly defined in terms of intermediate languages, where places for runtime 
type checking are explicitly stated in the forms of cast expressions. Examples 
of these intermediate languages include the blame calculus 
\citep{wadler2009well} 
and the cast calculus \citep{siek2009exploring}.
Representing casts naively, however, suffices sever space leak. 
For example, translation to intermediate languages can wrap some expressions 
with casts, including expressions at tail positions. Thus, mutually 
tail-recursive functions in source language can consume unbounded space at 
runtime. There are more examples of space leaking in \citet{herman2010space}.

@@

The relation between values is more special. When the \ineffCEKD\ value is 
non-casted, the casts in the \effCEK{C} value are identity. Otherwise, we push 
the cast into the value constructors, except injections. For examples: 
\begin{gather*}
\inference{
	v_1, v_2 : P &
	v_1 \approx v_2
}{
	\hcvOOinj{P_1}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
}
\quad
\inference{
	\Gamma , x : T_1 \vdash T_2 &
	\rho_1 \approx \rho_2
}{
	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
}
%\quad
%\inference{
%	\hcvOOcons{v_1}{c_1}{v_2}{c_2}
%	\approx
%	v
%}{
%	\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))}
%}
\\
\inference{
	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
}{
	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
	\approx
	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
}
\end{gather*}

>>>>

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -JS
  \\---\\
  Will fix grammar after fixing all other problems -KC}
\todo[inline]{The first paragraph of the introduction should summarize
  the entire introduction, and in some sense, the entire paper. -JS
\\---\\
Fixed -KC}

Around 2006, many work on integrating dynamic typing and static typing emerge, 
notably gradual types \citep{siek2006gradual} and hybrid types 
\citep{flanagan2006hybrid}. People usually define the semantics of gradually 
typed languages with intermediate languages that have cast expressions, such as
the blame calculus \citep{wadler2009well} and
the cast calculus \citep{siek2009exploring}. Casts are ubiquitous at runtime. 
For example, they can go in to values and continuations. Thus, representing 
casts naively with types can change asymptotically the space consumption of 
programs \citep{herman2010space}. There are several known space-efficient cast 
representations, but they have different strength and weakness. This paper 
presents a new solution that combines some of their best parts. Also, a valid 
cast representation must not change the result of programs. This paper presents 
the first framework for proving this kind of theorems.

%
%For example, translation to intermediate languages can wrap some expressions 
%with casts, including expressions at tail positions. Thus, mutually 
%tail-recursive functions in source language can consume unbounded space at 
%runtime. There are more examples of space leaking in \citet{herman2010space}.

@@

The relation between values is more special. When the \ineffCEKD\ value is 
non-casted, the casts in the \effCEK{C} value are identity. Otherwise, we push 
the cast into the value constructors, except injections. For examples: 
\begin{gather*}
\inference{
	v_1, v_2 : P &
	v_1 \approx v_2
}{
	\hcvOOinj{P_1}{v_1} \approx \vOOcast{v_2}{\cOOcast{P}{l}{\TOOdyn}}
}
\quad
\inference{
	\Gamma , x : T_1 \vdash T_2 &
	\rho_1 \approx \rho_2
}{z
	\hcvOOfun{id(T_1)}{\rho_1}{x}{e}{id(T_2)} \approx \vOOfun{\rho_2}{x}{e}
}
%\quad
%\inference{
%	\hcvOOcons{v_1}{c_1}{v_2}{c_2}
%	\approx
%	v
%}{
%	\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))}
%}
\\
\inference{
	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} : \POOfun{T_1}{T_2} &
	\hcvOOfun{c_1}{\rho}{x}{e}{c_2} \approx v
}{
	\hcvOOfun{seq(cast(T_3,l,T_1), c_1)}{\rho}{x}{e}{seq(c_2,cast(T_2,l,T_4))}
	\approx
	\vOOcast{v}{\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T3}{T_4}}}
}
\end{gather*}
\todo[inline]{need a more readable example -KC}
